Changes to police demand in COVID-19 pandemic

### 2022-03-24 docs/index.Rmd
final updates to n8 webinar slides

.pull-left[
![COVID19 and crime article](imgs/cov_news_03.png)
![COVID19 and crime article](imgs/cov_news_04.png)]

@@

> "… at the start of it, nobody really knew how it was going to affect them. I think there were a lot of people were quite genuinely scared that they were gonna maybe die from it." (interview 3)

> "We do get quite a lot of calls, sometimes about oh, you know the the neighbors are smoking drugs in the back garden, you know, sort of weed, that kind of thing." (interview 8)

@@

# Calls for information/reassurance

> "… in the first part of the first lockdown, people were very confused and very worried about breaking the law and very worried about being arrested for and they would ring up and say, can I do this and can I do that so people were actually asking our advice …" (interview 1)

# Calls for information/reassurance

@@

# Calls for information/reassurance

@@

# Support for such calls

> "We were directing people to the government website … We were we're not really qualified to advise people on the regulations that actually fit their particular area, because there was an area to area thing at certain times during the lockdown where different local councils and had different idea about the rules, interpreted the rules differently …" (interview 1)

# Support for such calls

@@

# Support for such calls

@@

> "Kickoffs, if if I can say that Saturday nights drunken night, yeah, those sort of thing, those sort of calls were a massive decrease." (interview 5)

@@

> "I don't really remember them being any higher in the lock downs than normal, and there were a lot of people were saying that all domestics have gone up, but I'm just guessing that people were spending so much time with each other forced that they're gonna have arguments. " (interview 6)

@@

@@

---
class: center, middle
# Further training outputs

@@

>>>>

.pull-left[
![COVID19 and crime article](imgs/cov_news_03.png)
![COVID19 and crime article](imgs/cov_news_04.png)
]

@@

@@

# Calls for information

@@

# Calls for reassurance

@@

# Support for such calls - direct to government website

@@

# Support for such calls - internal FAQ

@@

@@

@@

# Domestic incidents linked with NTE

@@

---
class: center, middle
# Sharing the learning

@@

---
class: center, middle, invesre

# Reflections on impact
